### 2020-05-26 writeup/intro.tex
intro
intro edits

	Our second theoretical insight is to show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
	We define \textit{data efficiency ratio} can be defined as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
	In Proposition \ref{prop_data_efficiency}, we consider an example and show that the data efficiency ratio is $\alert{\frac {1}{2\rho_t}}$.

>>>>

Our second theoretical insight is to show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
	We define the \textit{data efficiency ratio} as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
	In Proposition \ref{prop_data_efficiency}, we show that the data efficiency ratio of an illustrative example is at most $\alert{\frac {1}{2\rho_t}}$.
